### 2016-05-19 2016-lrec-tyvmorph/poster.tex
some more hargling, getting there....
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68636 72bbbca6-d526-0410-a7d9-f06f51895060

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\tiny}
\renewcommand*{\intitlepunct}{\space}

@@

	\headerbox{What should we put here}{name=harglebargle,column=0,below=morphtrans}{
		\begin{tabular}{lllll}
		\toprule
			stem & V & C & dative & genitive \\
		\midrule
			медаль & а & ль & медальга & медальдың \\
			ансамбль & а & бль & ансамбльге & ансамбльдиң \\
			руль & у & ль & рульга & рульдуң \\
			рубль & у & бль & рубльге & рубльдиң \\
		\bottomrule
		\end{tabular}
\codeex{\hilitegrey{"\{I\} harmony"\\
	\%\{I\%\}:Vy <=> :Vx [ :Cns* :RealCns ]/[ :0 | \%- ]* \_ ;}\\
	\-~~~~~~~~~except\\
	\-~~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь: :Cns* :RealCns ]/:0* \_ ;\\
	\-~~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь:0 ]/:[ :0 - ь: ]* \_ ;\\
	\-~~~~~~~~~\hilitegrey{where Vx in ( ү и е э ө а о ы у я ё ю )\\
	\-~~~~~~~~~~~~~~ Vy in ( ү и и и ү ы у ы у ы у у )\\
	\-~~~~~~~~~matched ;}\\
	\\
	"\{I\} always front when intervening Cль"\\
	\%\{I\%\}:и <=> [ :BackVow :Cns* :Cns :л ь: :Cns* :RealCns ]/:0* \_ ;\\
	\-~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь:0 ]/:[ :0 - ь: ]* \_ ;}
	}

@@

		}
	\headerbox{Evaluation}{name=results,column=2,below=morphotactics}{ %lexicon}{
		%\begin{multicols}{2}	
		\htwo{5-part corpus for naïve coverage}
		%\begin{itemize}
		%	\item Naïve coverage calculated on 5-part corpus
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\htwo{Precision and recall}
		%\begin{itemize}
		%	\item Good results reflect high accuracy
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak

		\htwo{Qualitative evaluation}
		%\begin{itemize}
		%	\item Qualitative evaluation
		%\end{itemize}

@@

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -0.5in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
		\end{itemize}
		\includegraphics[width=0.63\textwidth]{img/korp-2}
		\begin{itemize}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\vspace{1.45in}
		\dividerspace{}

>>>>

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,maxcitenames=2,style=authoryear,maxbibnames=99,uniquelist=false,uniquename=false]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\fontsize{5.75pt}{5.75pt}\selectfont}
\renewcommand*{\intitlepunct}{\space}

@@

	\headerbox{Finding out new linguistics things}{name=harglebargle,column=0,below=morphtrans}{
		\begin{center}
		\begin{tabular}{lllll}
		\toprule
			stem & V & C & dative & genitive \\
		\midrule
			медаль & а & ль & медальг\hiliteone{а} & медальд\hiliteone{ы}ң \\
			ансамбль & а & бль & ансамбльг\hilitetwo{е} & ансамбльд\hilitetwo{и}ң \\\midrule
			руль & у & ль & рульг\hiliteone{а} & рульд\hiliteone{у}ң \\
			рубль & у & бль & рубльг\hilitetwo{е} & рубльд\hilitetwo{и}ң \\
		\bottomrule
		\end{tabular}
		\end{center}\vspace{-0.5em}
\codeex{\hilitegrey{"\{I\} harmony"\\
	\%\{I\%\}:Vy <=> :Vx [ :Cns* :RealCns ]/[ :0 | \%- ]* \_ ;}\\
	\-~~~~~~~~~except\\
	\-~~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь: :Cns* :RealCns ]/:0* \_ ;\\
	\-~~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь:0 ]/:[ :0 - ь: ]* \_ ;\\
	\-~~~~~~~~~\hilitegrey{where Vx in ( ү и е э ө а о ы у я ё ю )\\
	\-~~~~~~~~~~~~~~ Vy in ( ү и и и ү ы у ы у ы у у )\\
	\-~~~~~~~~~matched ;}\\
	\\
	"\{I\} always front when intervening Cль"\\
	\%\{I\%\}:и <=> [ :BackVow :Cns* :Cns :л ь: :Cns* :RealCns ]/:0* \_ ;\\
	\-~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь:0 ]/:[ :0 - ь: ]* \_ ;}
	}

@@

		}
	\headerbox{Evaluation}{name=results,column=2,below=morphotactics}{ %lexicon}{
		%\begin{multicols}{2}	
		\htwo{5-part corpus for naïve coverage}
		\vspace{-0.2em}
		%\begin{itemize}
		%	\item Naïve coverage calculated on 5-part corpus
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{lrr}
			\toprule
			 \textbf{Domain} & \textbf{Tokens} & \textbf{Coverage} (\%) \\
			\midrule
			 News       & 1,539,459 &  95.73  \\
			 Religion   & 746,124 &  93.84 \\
			 Literature & 297,830 &  91.96  \\
			 Encyclopaedic  & 276,547 & 90.86 \\
			 Folklore & 27,902 & 91.57  \\\cline{2-3}
			 Average    & -- & 92.79 \\
			\bottomrule
		\end{tabular}}
		\end{center}

		\htwo{Precision and recall}
		\vspace{-0.2em}
		%\begin{itemize}
		%	\item Good results reflect high accuracy
		%\end{itemize}
		\begin{center}
		\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{llrr}
			\toprule
				& \textbf{count} & \textbf{precision} & \textbf{recall} \\
			\midrule
			known tokens & 1024 & 0.99 & 0.97 \\
			all tokens & 1425 & 0.99 & 0.69 \\
			\bottomrule
		\end{tabular}}
		\end{center}
		%{\qipa ↑} quantitative eval\\
		%\newline
		%\vspace{0.01pt}\hfill{}qualitative eval {\qipa ↗}\\
		%\columnbreak

		\htwo{Qualitative evaluation}
		\vspace{-0.2em}
		%\begin{itemize}
		%	\item Qualitative evaluation
		%\end{itemize}

@@

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -1in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\includegraphics[width=0.63\textwidth]{img/korp-2}
		%\begin{itemize}
		%\end{itemize}
		\vspace{1.55in}
		\dividerspace{}
